Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-06 tese2/abstract.tex

\ac{WebRTC} technology allows real-time communications between web browsers without the need to install and use additional applications or plug-ins. The nature of web browser applications already follows the hypermedia concept, which makes \ac{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
{\color{blue}The web browser platform provides an abstraction layer that makes it possible to create applications that run independently from the operating system.}
The native support for \ac{WebRTC} in operating systems extends its usage to outside the web browser, allowing for the exploration of functionalities for which web browsers provide poor support, such as video recording and massive information storage.

@@

{\color{red}Our goal in this project is to develop an application targeted to the web platform, resorting to \ac{WebRTC}, that leverages the hyper-linked communications by providing a video conference environment enriched with interactive and non-interactive discrete media types such as images, subtitles, forms and all types of content that can be added using \emph{HTML5}, \emph{CSS3} and \emph{JavaScript} including continuous media types such as video, music and animations.}

@@

{\color{blue}
In this document, we present the current State Of The Art in hyper-linked communications and related technologies, propose and implement an architecture for an hyper-linked communication application based on \ac{WebRTC} and provide the results for its implementation and evaluation.
}

>>>>

\emph{WebRTC} technology allows real-time communications between web browsers without the need to install and use additional applications or plug-ins. The nature of web browser applications already follows the hypermedia concept, which makes \emph{WebRTC} the ideal technology to apply the hyper-linked communications concepts.
{\color{blue}The web browser platform provides an abstraction layer that makes it possible to create applications that run independently from the operating system.}
The native support for \emph{WebRTC} in operating systems extends its usage to outside the web browser, allowing for the exploration of functionalities for which web browsers provide poor support, such as video recording and massive information storage.

@@

{\color{red}Our goal in this project is to develop an application targeted to the web platform, resorting to \emph{WebRTC}, that leverages the hyper-linked communications by providing a video conference environment enriched with interactive and non-interactive discrete media types.}

@@

{\color{blue}
In this document, we present the current State Of The Art in hyper-linked communications and related technologies, propose and implement an architecture for an hyper-linked communication application based on \emph{WebRTC} and provide the results for its implementation and evaluation.
}
